---
title: "RQ1: Discussion Participation"
subtitle: "Reddit Communities Field Experiment"
output: html_document
date: "`r Sys.Date()`"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, out.width = "90%", out.height = "70%",message=F, warning=F)
```

```{r}
library(tidyverse)
library(readr)
library(gridExtra)
library(haven)
library(RColorBrewer)
library(estimatr)
library(ggridges)
library(DescTools)
library(lme4)
library(brms)
library(purrr)
library(tableone)
library(pscl)
library(ggcorrplot)
library(kableExtra)
```

Import data (no comment texts, open comments, usernames or email addresses)
```{r}
# reddit data
user_data <- read_csv("../data/anon/users_anon.csv")
discussion_data <- read_csv("../data/anon/discussions_anon.csv")
external_data <- read_csv("../data/anon/external_reddit_anon.csv")

# survey data
pre_survey <- read_csv("../data/anon/pre_survey_anon.csv")
post_surveys <- read_csv("../data/anon/post_surveys_anon.csv")

# sample (combined data)
sample <- read_csv("../data/anon/sample_anon.csv")
```

Preprocessing, combining pre and post surveys 
```{r}
# average group toxicity
group_toxicity_dat <- discussion_data%>%
  mutate(subreddit_w1 = subreddit)%>%
  group_by(subreddit_w1)%>%
  mutate(group_toxicity = mean(comment_toxicity, na.rm=T))%>%
  select(subreddit_w1, group_toxicity)%>%
  slice(1)%>%
  ungroup()

# any check-in surveys answered
any_check <- post_surveys%>%
  group_by(ParticipantID)%>%
  mutate(any_checkin = 1)%>%
  slice(1)%>%
  pull(ParticipantID)

post_1 <- post_surveys%>%filter(survey_week == 1)
post_2 <- post_surveys%>%filter(survey_week == 2)
post_3 <- post_surveys%>%filter(survey_week == 3)
post_4 <- post_surveys%>%filter(survey_week == 4)

# pre-post data (combining pre and post surveys) 
full_data <- left_join(sample, post_1, by = "ParticipantID", suffix = c("_w1" , "_w2"))%>%
  left_join(., post_2, by = "ParticipantID", suffix = c("" , "_w3"))%>%
  left_join(., post_3, by = "ParticipantID", suffix = c("" , "_w4"))%>%
  left_join(., post_4, by = "ParticipantID", suffix = c("" , "_w5"))%>%
  left_join(.,group_toxicity_dat, by = "subreddit_w1")%>%
  mutate(active = ifelse(is.na(comment_count), 0, 1),
         condition = factor(condition),
         active2 = ifelse(!ParticipantID %in% any_check & active == 0, "inactive", active))

write_csv(full_data, file = "../data/anon/full_data_waves.csv")
```

Data Scaling for models 
https://onlinelibrary.wiley.com/doi/10.1002/sim.3107
```{r}
# scale data for better comparison of coefficients
gelman_scale <- function(x){
  ( (x - mean(x, na.rm=T)) / (2*sd(x, na.rm=TRUE)))
}

scaled_sample <- full_data%>%
  # generation of check-in variables (average over check-ins)
  mutate(mean_issue_distance_abs = rowMeans(select(., starts_with("issue_distance_abs")), na.rm = TRUE),
         mean_discussion_constructive = rowMeans(select(., starts_with("discussion_percep_2")), na.rm = TRUE),
         mean_discussion_enjoyable = rowMeans(select(., starts_with("discussion_percep_3")), na.rm = TRUE),
         mean_discussion_toxic = rowMeans(select(., starts_with("discussion_percep_1")), na.rm = TRUE),
         mean_group_knowledgeable = rowMeans(select(., starts_with("group_percep_3")), na.rm = TRUE), 
         mean_group_polarized = rowMeans(select(., starts_with("group_percep_2")), na.rm = TRUE),
         mean_group_respectful = rowMeans(select(., starts_with("group_percep_1")), na.rm = TRUE))%>%
  # scale selected variables with Gelman (2008) method by dividing by two standard deviations
  select(ParticipantID, condition, subreddit_w1, comment_count, comment_mean_tox, active, active2, gender, age, education, comments_online_w1,  group_toxicity,
         leftright_w1, polinterest_w1, affective_polarization_w1, 
         affective_pol_1_w1,affective_pol_2_w1,comment_karma,
         pol_cynicism_w1, efficacy_w1, trust_general_1_w1,
         trust_general_2_w1,trust_general_3_w1,trust_general_4_w1,
         mean_issue_distance_abs, mean_discussion_constructive, 
         mean_discussion_enjoyable, mean_discussion_toxic, 
         mean_group_knowledgeable, mean_group_polarized, 
         mean_group_respectful)%>%
  mutate(across(c(age:mean_group_respectful), gelman_scale))%>%
  mutate(comment_count = ifelse(is.na(comment_count),0,comment_count),
         gender_male = factor(ifelse(gender == 1, 1, 0)))

write_csv(scaled_sample, file = "../data/anon/scaled_sample.csv")
```

# Participation Prediction

## Zero Hurdle Models for Count data
https://en.wikipedia.org/wiki/Hurdle_model
https://search.r-project.org/CRAN/refmans/pscl/html/hurdle.html

```{r}
# correspondence between perceptions and external measures
cor.test(scaled_sample$mean_discussion_toxic, scaled_sample$group_toxicity)

present_sample <- scaled_sample%>%
  filter(active2 != "inactive")%>%
  # also include external measure of group toxicity
  mutate(group_toxicity = gelman_scale(group_toxicity)) 

models <- list(
  hurdle(comment_count ~ gender_male, data = present_sample),
  hurdle(comment_count ~ age, data = present_sample),
  hurdle(comment_count ~ education, data = present_sample),
  hurdle(comment_count ~ comments_online_w1, data = present_sample),
  hurdle(comment_count ~ comment_karma, data = present_sample),
  hurdle(comment_count ~ leftright_w1, data = present_sample),
  hurdle(comment_count ~ polinterest_w1, data = present_sample),
  hurdle(comment_count ~ affective_polarization_w1, data = present_sample),
  hurdle(comment_count ~ trust_general_1_w1, data = present_sample),
  hurdle(comment_count ~ trust_general_2_w1, data = present_sample),
  hurdle(comment_count ~ trust_general_3_w1, data = present_sample),
  hurdle(comment_count ~ trust_general_4_w1, data = present_sample),
  hurdle(comment_count ~ mean_issue_distance_abs, data = present_sample),
  hurdle(comment_count ~ mean_group_respectful, data = present_sample),
  hurdle(comment_count ~ mean_group_knowledgeable, data = present_sample),
  hurdle(comment_count ~ mean_group_polarized, data = present_sample),
  hurdle(comment_count ~ mean_discussion_enjoyable, data = present_sample),
  hurdle(comment_count ~ mean_discussion_constructive, data = present_sample),
  hurdle(comment_count ~ mean_discussion_toxic, data = present_sample),
  hurdle(comment_count ~ group_toxicity, data = present_sample)
)

predictors <- c(
  "Gender (male)", "Age", "Education", "Commenting online", "Comment karma", "Political orientation",
  "Political interest", "Affective polarization", "Trust in politics","Trust in media",
  "Trust in science", "Trust in others", "Issue distance",
  "Group respectful", "Group knowledgeable", "Group polarized",
  "Discussion enjoyable",  "Discussion constructive","Discussion toxic",
   "Average group toxicity")

model_frames <- list()

for (i in seq_along(models)) {
  model_summary <- summary(models[[i]])
  
  count_model_coef <- as.data.frame(model_summary$coefficients$count)
  count_model_coef$Predictor <- predictors[i]
  count_model_coef$Model <- "Count Model"
  count_model_coef <- count_model_coef %>%
    filter(row.names(.) != "(Intercept)") %>%
    rename(Coefficient = Estimate, SE = `Std. Error`, pval = `Pr(>|z|)`)
  
  zero_hurdle_coef <- as.data.frame(model_summary$coefficients$zero)
  zero_hurdle_coef$Predictor <- predictors[i]
  zero_hurdle_coef$Model <- "Zero Hurdle Model"
  zero_hurdle_coef <- zero_hurdle_coef %>%
    filter(row.names(.) != "(Intercept)") %>%
    rename(Coefficient = Estimate, SE = `Std. Error`, pval = `Pr(>|z|)`)
  
  model_frames[[i]] <- rbind(count_model_coef, zero_hurdle_coef)
}

combined_df <- do.call(rbind, model_frames)

combined_df <- combined_df %>%
  mutate(Predictor = fct_inorder(rev(Predictor))) %>%
  group_by(Model) %>%
  mutate(AlphaValue = abs(Coefficient) / max(abs(Coefficient), na.rm = TRUE)) %>%
  ungroup()

interval2 <- -qnorm((1 - 0.95) / 2)

comment_plot_pred_active_hurdle_ext <- ggplot(combined_df, aes(x = rev(Predictor), alpha = abs(AlphaValue))) + 
  geom_hline(yintercept = 0, colour = gray(1 / 2), lty = 2) + 
  geom_pointrange(aes(y = Coefficient, ymin = Coefficient - SE * interval2,
                      ymax = Coefficient + SE * interval2), colour = "black",
                  lwd = 1, position = position_dodge(width = 2 / 3)) + 
  guides(alpha = "none") +
  theme_bw(base_size = 10) + 
  coord_flip() +
  ggtitle("Prediction of user level discussion participation") +
  xlab("") +
  ylab("Zero hurdle models for count data regression") +
  facet_wrap(~ Model, ncol = 2, scales = "free_x")  

ggsave("../output/comment_plot_pred_hurdle_with_external.pdf", comment_plot_pred_active_hurdle_ext, width = 6, height = 4)

comment_plot_pred_active_hurdle_ext
```

### Geometric distribution (instead of default poisson)
```{r}
models <- list(
  hurdle(comment_count ~ gender_male, data = present_sample, dist = "geometric"),
  hurdle(comment_count ~ age, data = present_sample, dist = "geometric"),
  hurdle(comment_count ~ education, data = present_sample, dist = "geometric"),
  hurdle(comment_count ~ comments_online_w1, data = present_sample, dist = "geometric"),
  hurdle(comment_count ~ comment_karma, data = present_sample, dist = "geometric"),
  hurdle(comment_count ~ leftright_w1, data = present_sample, dist = "geometric"),
  hurdle(comment_count ~ polinterest_w1, data = present_sample, dist = "geometric"),
  hurdle(comment_count ~ affective_polarization_w1, data = present_sample, dist = "geometric"),
  hurdle(comment_count ~ trust_general_1_w1, data = present_sample, dist = "geometric"),
  hurdle(comment_count ~ trust_general_2_w1, data = present_sample, dist = "geometric"),
  hurdle(comment_count ~ trust_general_3_w1, data = present_sample, dist = "geometric"),
  hurdle(comment_count ~ trust_general_4_w1, data = present_sample, dist = "geometric"),
  hurdle(comment_count ~ mean_issue_distance_abs, data = present_sample, dist = "geometric"),
  hurdle(comment_count ~ mean_group_respectful, data = present_sample, dist = "geometric"),
  hurdle(comment_count ~ mean_group_knowledgeable, data = present_sample, dist = "geometric"),
  hurdle(comment_count ~ mean_group_polarized, data = present_sample, dist = "geometric"),
  hurdle(comment_count ~ mean_discussion_enjoyable, data = present_sample, dist = "geometric"),
  hurdle(comment_count ~ mean_discussion_toxic, data = present_sample, dist = "geometric"),
  hurdle(comment_count ~ mean_discussion_constructive, data = present_sample, dist = "geometric")
)

predictors <- c(
  "Gender (male)", "Age", "Education", "Commenting online", "Comment karma", "Political orientation",
  "Political interest", "Affective polarization", "Trust in politics", "Trust in media",
  "Trust in science", "Trust in others", "Issue distance",
  "Group respectful", "Group knowledgeable", "Group polarized",
  "Discussion enjoyable", "Discussion toxic", "Discussion constructive"
)

model_frames <- list()

for (i in seq_along(models)) {
  model_summary <- summary(models[[i]])
  
  count_model_coef <- as.data.frame(model_summary$coefficients$count)
  count_model_coef$Predictor <- predictors[i]
  count_model_coef$Model <- "Count Model"  
  count_model_coef <- count_model_coef %>% 
    filter(row.names(.) != "(Intercept)") %>%   
    rename(Coefficient = Estimate, SE = `Std. Error`, pval = `Pr(>|z|)`)
  
  zero_hurdle_coef <- as.data.frame(model_summary$coefficients$zero)
  zero_hurdle_coef$Predictor <- predictors[i]
  zero_hurdle_coef$Model <- "Zero Hurdle Model"  
  zero_hurdle_coef <- zero_hurdle_coef %>% 
    filter(row.names(.) != "(Intercept)") %>%   
    rename(Coefficient = Estimate, SE = `Std. Error`, pval = `Pr(>|z|)`)
  
  model_frames[[i]] <- rbind(count_model_coef, zero_hurdle_coef)
}

combined_df <- do.call(rbind, model_frames)

combined_df <- combined_df %>%
  mutate(Predictor = fct_inorder(rev(Predictor))) %>%
  group_by(Model) %>%
  mutate(AlphaValue = abs(Coefficient) / max(abs(Coefficient), na.rm = TRUE)) %>%
  ungroup()

comment_plot_pred_active_hurdle_geometric <- ggplot(combined_df, aes(x = rev(Predictor), alpha = abs(AlphaValue))) + 
  geom_hline(yintercept = 0, colour = gray(1 / 2), lty = 2) + 
  geom_pointrange(aes(y = Coefficient, ymin = Coefficient - SE * interval2,
                      ymax = Coefficient + SE * interval2), colour = "black",
                  lwd = 1, position = position_dodge(width = 2 / 3)) + 
  guides(alpha = "none") +
  theme_bw(base_size = 10) + 
  coord_flip() +
  ggtitle("Prediction of user level discussion participation") +
  xlab("") +
  ylab("Zero hurdle models for count data regression (geometric, binomial)") +
  facet_wrap(~ Model, ncol = 2, scales = "free_x")  

ggsave("../output/comment_plot_pred_hurdle_geometric.pdf", comment_plot_pred_active_hurdle_geometric, width = 6, height = 4)

comment_plot_pred_active_hurdle_geometric
```

### Negative Binomial
```{r}
models <- list(
  hurdle(comment_count ~ gender_male, data = present_sample, dist = "negbin"),
  hurdle(comment_count ~ age, data = present_sample, dist = "negbin"),
  hurdle(comment_count ~ education, data = present_sample, dist = "negbin"),
  hurdle(comment_count ~ comments_online_w1, data = present_sample, dist = "negbin"),
  hurdle(comment_count ~ comment_karma, data = present_sample, dist = "negbin"),
  hurdle(comment_count ~ leftright_w1, data = present_sample, dist = "negbin"),
  hurdle(comment_count ~ polinterest_w1, data = present_sample, dist = "negbin"),
  hurdle(comment_count ~ affective_polarization_w1, data = present_sample, dist = "negbin"),
  hurdle(comment_count ~ trust_general_1_w1, data = present_sample, dist = "negbin"),
  hurdle(comment_count ~ trust_general_2_w1, data = present_sample, dist = "negbin"),
  hurdle(comment_count ~ trust_general_3_w1, data = present_sample, dist = "negbin"),
  hurdle(comment_count ~ trust_general_4_w1, data = present_sample, dist = "negbin"),
  hurdle(comment_count ~ mean_issue_distance_abs, data = present_sample, dist = "negbin"),
  hurdle(comment_count ~ mean_group_respectful, data = present_sample, dist = "negbin"),
  hurdle(comment_count ~ mean_group_knowledgeable, data = present_sample, dist = "negbin"),
  hurdle(comment_count ~ mean_group_polarized, data = present_sample, dist = "negbin"),
  hurdle(comment_count ~ mean_discussion_enjoyable, data = present_sample, dist = "negbin"),
  hurdle(comment_count ~ mean_discussion_toxic, data = present_sample, dist = "negbin"),
  hurdle(comment_count ~ mean_discussion_constructive, data = present_sample, dist = "negbin")
)

model_frames <- list()

for (i in seq_along(models)) {
  model_summary <- summary(models[[i]])
  
  count_model_coef <- as.data.frame(model_summary$coefficients$count)
  count_model_coef$Predictor <- predictors[i]
  count_model_coef$Model <- "Count Model"  
  count_model_coef <- count_model_coef %>% 
    filter(row.names(.) != "(Intercept)") %>% 
    rename(Coefficient = Estimate, SE = `Std. Error`, pval = `Pr(>|z|)`)
  
  zero_hurdle_coef <- as.data.frame(model_summary$coefficients$zero)
  zero_hurdle_coef$Predictor <- predictors[i]
  zero_hurdle_coef$Model <- "Zero Hurdle Model" 
  zero_hurdle_coef <- zero_hurdle_coef %>% 
    filter(row.names(.) != "(Intercept)") %>% 
    rename(Coefficient = Estimate, SE = `Std. Error`, pval = `Pr(>|z|)`)
  
  model_frames[[i]] <- rbind(count_model_coef, zero_hurdle_coef)
}

combined_df <- do.call(rbind, model_frames)

combined_df <- combined_df %>%
  rownames_to_column()%>%
  filter(!str_detect(rowname,"theta"))%>%
  mutate(Predictor = fct_inorder(rev(Predictor))) %>%
  group_by(Model) %>%
  mutate(AlphaValue = abs(Coefficient) / max(abs(Coefficient), na.rm = TRUE)) %>%
  ungroup()

comment_plot_pred_active_hurdle_negbin <- ggplot(combined_df, aes(x = rev(Predictor), alpha = abs(AlphaValue))) + 
  geom_hline(yintercept = 0, colour = gray(1 / 2), lty = 2) + 
  geom_pointrange(aes(y = Coefficient, ymin = Coefficient - SE * interval2,
                      ymax = Coefficient + SE * interval2), colour = "black",
                  lwd = 1, position = position_dodge(width = 2 / 3)) + 
  guides(alpha = "none") +
  theme_bw(base_size = 10) + 
  coord_flip() +
  ggtitle("Prediction of user level discussion participation") +
  xlab("") +
  ylab("Zero hurdle models for count data regression (negbin, binomial)") +
  facet_wrap(~ Model, ncol = 2, scales = "free_x")  

# Save the plot with "negbin" in the file name
ggsave("../output/comment_plot_pred_hurdle_negbin.pdf", comment_plot_pred_active_hurdle_negbin, width = 6, height = 4)

# Display the plot
comment_plot_pred_active_hurdle_negbin
```

### Binary Active vs. Passive 
```{r}
models <- list(
  glm(active ~ gender_male, data = present_sample),
  glm(active ~ age, data = present_sample),
  glm(active ~ education, data = present_sample),
  glm(active ~ comments_online_w1, data = present_sample),
  glm(active ~ comment_karma, data = present_sample),
  glm(active ~ leftright_w1, data = present_sample),
  glm(active ~ polinterest_w1, data = present_sample),
  glm(active ~ affective_polarization_w1, data = present_sample),
  glm(active ~ trust_general_1_w1, data = present_sample),
  glm(active ~ trust_general_2_w1, data = present_sample),
  glm(active ~ trust_general_3_w1, data = present_sample),
  glm(active ~ trust_general_4_w1, data = present_sample),
  glm(active ~ mean_issue_distance_abs, data = present_sample),
  glm(active ~ mean_group_respectful, data = present_sample),
  glm(active ~ mean_group_knowledgeable, data = present_sample),
  glm(active ~ mean_group_polarized, data = present_sample),
  glm(active ~ mean_discussion_enjoyable, data = present_sample),
  glm(active ~ mean_discussion_toxic, data = present_sample),
  glm(active ~ mean_discussion_constructive, data = present_sample)
)

model_frames <- list()

for (i in seq_along(models)) {
  model_frames[[i]] <- data.frame(
    Coefficient = summary(models[[i]])$coef[-1, 1], 
    pval = summary(models[[i]])$coef[,4],
    SE = summary(models[[i]])$coef[-1, 2],          
    Predictor = predictors[i]                     
  )
}

combined_df <- do.call(rbind, model_frames)
combined_df <- combined_df%>%
  mutate(Significance = ifelse(pval < 0.05, "sig.", "insig."),
         Predictor = fct_inorder(rev(Predictor)))%>%
  group_by(Predictor)%>%
  slice(2) 

comment_plot_pred_binary <- ggplot(combined_df, aes(x = rev(Predictor), alpha = abs(Coefficient))) + 
  geom_hline(yintercept = 0, colour = gray(1/2), lty = 2) + 
  geom_pointrange(aes(y = Coefficient, ymin = Coefficient - SE*interval2,
                      ymax = Coefficient + SE*interval2), colour = "black",
                  lwd = 1, position = position_dodge(width = 2/3)) + 
  guides(alpha = "none")+
  theme_bw(base_size=10)+ 
  coord_flip()+
  ggtitle("Comment activity binary", subtitle = "Excluding inactive users")+
  xlab("")+
  ylab("Change in log odds")

comment_plot_pred_binary

ggsave("../output/comment_plot_pred_binary.pdf",comment_plot_pred_binary, width = 4, height = 4)
```

### Manual poisson models for count data (active only)
```{r}
present_sample <- scaled_sample%>%filter(active == 1)

models <- list(
  glm(comment_count ~ gender_male, family = poisson(link = "log"), data = present_sample),
  glm(comment_count ~ age, family = poisson(link = "log"), data = present_sample),
  glm(comment_count ~ education, family = poisson(link = "log"), data = present_sample),
  glm(comment_count ~ comments_online_w1, family = poisson(link = "log"), data = present_sample),
  glm(comment_count ~ comment_karma, family = poisson(link = "log"), data = present_sample),
  glm(comment_count ~ leftright_w1, family = poisson(link = "log"), data = present_sample),
  glm(comment_count ~ polinterest_w1, family = poisson(link = "log"), data = present_sample),
  glm(comment_count ~ affective_polarization_w1, family = poisson(link = "log"), data = present_sample),
  glm(comment_count ~ trust_general_1_w1, family = poisson(link = "log"), data = present_sample),
  glm(comment_count ~ trust_general_2_w1, family = poisson(link = "log"), data = present_sample),
  glm(comment_count ~ trust_general_3_w1, family = poisson(link = "log"), data = present_sample),
  glm(comment_count ~ trust_general_4_w1, family = poisson(link = "log"), data = present_sample),
  glm(comment_count ~ mean_issue_distance_abs, family = poisson(link = "log"), data = present_sample),
  glm(comment_count ~ mean_group_respectful, family = poisson(link = "log"), data = present_sample),
  glm(comment_count ~ mean_group_knowledgeable, family = poisson(link = "log"), data = present_sample),
  glm(comment_count ~ mean_group_polarized, family = poisson(link = "log"), data = present_sample),
  glm(comment_count ~ mean_discussion_enjoyable, family = poisson(link = "log"), data = present_sample),
  glm(comment_count ~ mean_discussion_toxic, family = poisson(link = "log"), data = present_sample),
  glm(comment_count ~ mean_discussion_constructive, family = poisson(link = "log"), data = present_sample)
)

model_frames <- list()

for (i in seq_along(models)) {
  model_summary <- summary(models[[i]])
    model_frames[[i]] <- data.frame(
    Coefficient = model_summary$coef[-1, 1],        
    pval = model_summary$coef[-1, 4],               
    SE = model_summary$coef[-1, 2],                 
    Predictor = predictors[i]                       
  )
}


combined_df <- do.call(rbind, model_frames)
combined_df <- combined_df %>%
  mutate(Predictor = fct_inorder(rev(Predictor)))

comment_plot_pred_active <- ggplot(combined_df, aes(x = rev(Predictor), alpha = abs(Coefficient))) + 
  geom_hline(yintercept = 0, colour = gray(1 / 2), lty = 2) + 
  geom_pointrange(aes(y = Coefficient, ymin = Coefficient - SE * interval2,
                      ymax = Coefficient + SE * interval2), colour = "black",
                  lwd = 1 , position = position_dodge(width = 2 / 3)) + 
  guides(alpha = "none") +
  theme_bw(base_size = 10) + 
  coord_flip() +
  ggtitle("Comment activity", subtitle = "Poisson prediction of comment count") +
  xlab("") +
  ylab("Change in log number of comments")

comment_plot_pred_active

ggsave("../output/comment_plot_pred_poisson.pdf", comment_plot_pred_active, width = 4, height = 4)
```


### Linear models (Excluding 0 and inactive)
```{r}
present_sample <- scaled_sample%>%filter(active == 1)

mean(present_sample$comment_count)
sd(present_sample$comment_count)
max(present_sample$comment_count)

models <- list(
  lm_robust(comment_count ~ gender_male, data = present_sample),
  lm_robust(comment_count ~ age, data = present_sample),
  lm_robust(comment_count ~ education, data = present_sample),
  lm_robust(comment_count ~ comments_online_w1, data = present_sample),
  lm_robust(comment_count ~ comment_karma, data = present_sample),
  lm_robust(comment_count ~ leftright_w1, data = present_sample),
  lm_robust(comment_count ~ polinterest_w1, data = present_sample),
  lm_robust(comment_count ~ affective_polarization_w1, data = present_sample),
  lm_robust(comment_count ~ trust_general_1_w1, data = present_sample),
  lm_robust(comment_count ~ trust_general_2_w1, data = present_sample),
  lm_robust(comment_count ~ trust_general_3_w1, data = present_sample),
  lm_robust(comment_count ~ trust_general_4_w1, data = present_sample),
  lm_robust(comment_count ~ mean_issue_distance_abs, data = present_sample),
  lm_robust(comment_count ~ mean_group_respectful, data = present_sample),
  lm_robust(comment_count ~ mean_group_knowledgeable, data = present_sample),
  lm_robust(comment_count ~ mean_group_polarized, data = present_sample),
  lm_robust(comment_count ~ mean_discussion_enjoyable, data = present_sample),
  lm_robust(comment_count ~ mean_discussion_toxic, data = present_sample),
  lm_robust(comment_count ~ mean_discussion_constructive, data = present_sample)
)

model_frames <- list()

for (i in seq_along(models)) {
  model_frames[[i]] <- data.frame(
    Coefficient = summary(models[[i]])$coef[-1, 1],  
    pval = summary(models[[i]])$coef[,4],
    SE = summary(models[[i]])$coef[-1, 2],         
    Predictor = predictors[i]                       
  )
}

combined_df <- do.call(rbind, model_frames)
combined_df <- combined_df%>%
  mutate(Significance = ifelse(pval < 0.05, "sig.", "insig."),
         Predictor = fct_inorder(rev(Predictor)))%>%
  group_by(Predictor)%>%
  slice(2) 


comment_plot_pred_active_ex0 <- ggplot(combined_df, aes(x = rev(Predictor), alpha = abs(Coefficient))) + 
  geom_hline(yintercept = 0, colour = gray(1/2), lty = 2) + 
  geom_pointrange(aes(y = Coefficient, ymin = Coefficient - SE*interval2,
                      ymax = Coefficient + SE*interval2), colour = "black",
                  lwd = 1/2, position = position_dodge(width = 2/3)) + 
  guides(alpha = "none")+
  theme_bw(base_size=10)+ 
  coord_flip()+
  ggtitle("Comment activity", subtitle = "Linear prediction of comment count")+
  xlab("")+
  ylab("Scaled beta coefficients, HC2 robust SE")

comment_plot_pred_active_ex0

ggsave("../output/comment_plot_pred_active_excl0.pdf",comment_plot_pred_active_ex0, width = 4, height = 4)
```


# Hurdle models for different experimental conditions (start RQ2)
```{r, fig.width=6, fig.height=12}
present_sample <- scaled_sample%>%filter(active2 != "inactive")

# filtered data for control condition
scaled_sample_c <- present_sample %>% filter(condition == "control")

# models for control condition
models_control <- list(
  hurdle(comment_count ~ gender_male, data = scaled_sample_c),
  hurdle(comment_count ~ age, data = scaled_sample_c),
  hurdle(comment_count ~ education, data = scaled_sample_c),
  hurdle(comment_count ~ comments_online_w1, data = scaled_sample_c),
  hurdle(comment_count ~ comment_karma, data = scaled_sample_c),
  hurdle(comment_count ~ leftright_w1, data = scaled_sample_c),
  hurdle(comment_count ~ polinterest_w1, data = scaled_sample_c),
  hurdle(comment_count ~ affective_polarization_w1, data = scaled_sample_c),
  hurdle(comment_count ~ trust_general_1_w1, data = scaled_sample_c),
  hurdle(comment_count ~ trust_general_2_w1, data = scaled_sample_c),
  hurdle(comment_count ~ trust_general_3_w1, data = scaled_sample_c),
  hurdle(comment_count ~ trust_general_4_w1, data = scaled_sample_c),
  hurdle(comment_count ~ mean_issue_distance_abs, data = scaled_sample_c),
  hurdle(comment_count ~ mean_group_respectful, data = scaled_sample_c),
  hurdle(comment_count ~ mean_group_knowledgeable, data = scaled_sample_c),
  hurdle(comment_count ~ mean_group_polarized, data = scaled_sample_c),
  hurdle(comment_count ~ mean_discussion_enjoyable, data = scaled_sample_c),
  hurdle(comment_count ~ mean_discussion_toxic, data = scaled_sample_c),
  hurdle(comment_count ~ mean_discussion_constructive, data = scaled_sample_c)
)

model_frames_control <- list()

for (i in seq_along(models_control)) {
  model_summary <- summary(models_control[[i]])
  
  count_model_coef <- as.data.frame(model_summary$coefficients$count)
  count_model_coef$Predictor <- predictors[i]
  count_model_coef$Model <- "Count Model"  
  count_model_coef <- count_model_coef %>% 
    filter(row.names(.) != "(Intercept)") %>% 
    rename(Coefficient = Estimate, SE = `Std. Error`, pval = `Pr(>|z|)`)
  
  zero_hurdle_coef <- as.data.frame(model_summary$coefficients$zero)
  zero_hurdle_coef$Predictor <- predictors[i]
  zero_hurdle_coef$Model <- "Zero Hurdle Model"  
  zero_hurdle_coef <- zero_hurdle_coef %>% 
    filter(row.names(.) != "(Intercept)") %>% 
    rename(Coefficient = Estimate, SE = `Std. Error`, pval = `Pr(>|z|)`)
  
  model_frames_control[[i]] <- rbind(count_model_coef, zero_hurdle_coef)
}

combined_df_control <- bind_rows(model_frames_control) %>%
  mutate(Significance = ifelse(pval < 0.05, "sig.", "insig."),
         Predictor = fct_inorder(rev(Predictor))) %>%
  group_by(Model) %>%
  mutate(AlphaValue = abs(Coefficient) / max(abs(Coefficient), na.rm = TRUE)) %>%
  ungroup()

comment_plot_pred_c <- ggplot(combined_df_control, aes(x = rev(Predictor), alpha = AlphaValue)) +
  geom_hline(yintercept = 0, colour = gray(1/2), lty = 2) +
  geom_pointrange(aes(y = Coefficient, ymin = Coefficient - SE * interval2,
                      ymax = Coefficient + SE * interval2), colour = "#70facb", lwd = 1) +
  guides(alpha = "none") +
  theme_bw(base_size = 10) +
  coord_flip() +
  facet_wrap(~ Model, ncol = 2, scales = "free_x") +
  ggtitle("Control condition", subtitle = "Prediction of user level discussion participation") +
  xlab("") +
  ylab("Zero hurdle models for count data regression")


# filtered data for moderation condition
scaled_sample_m <- present_sample %>% filter(condition == "moderation")

# Models for moderation condition
models_moderation <- list(
  hurdle(comment_count ~ gender_male, data = scaled_sample_m),
  hurdle(comment_count ~ age, data = scaled_sample_m),
  hurdle(comment_count ~ education, data = scaled_sample_m),
  hurdle(comment_count ~ comments_online_w1, data = scaled_sample_m),
  hurdle(comment_count ~ comment_karma, data = scaled_sample_m),
  hurdle(comment_count ~ leftright_w1, data = scaled_sample_m),
  hurdle(comment_count ~ polinterest_w1, data = scaled_sample_m),
  hurdle(comment_count ~ affective_polarization_w1, data = scaled_sample_m),
  hurdle(comment_count ~ trust_general_1_w1, data = scaled_sample_m),
  hurdle(comment_count ~ trust_general_2_w1, data = scaled_sample_m),
  hurdle(comment_count ~ trust_general_3_w1, data = scaled_sample_m),
  hurdle(comment_count ~ trust_general_4_w1, data = scaled_sample_m),
  hurdle(comment_count ~ mean_issue_distance_abs, data = scaled_sample_m),
  hurdle(comment_count ~ mean_group_respectful, data = scaled_sample_m),
  hurdle(comment_count ~ mean_group_knowledgeable, data = scaled_sample_m),
  hurdle(comment_count ~ mean_group_polarized, data = scaled_sample_m),
  hurdle(comment_count ~ mean_discussion_enjoyable, data = scaled_sample_m),
  hurdle(comment_count ~ mean_discussion_toxic, data = scaled_sample_m),
  hurdle(comment_count ~ mean_discussion_constructive, data = scaled_sample_m)
)


model_frames_moderation <- list()
for (i in seq_along(models_moderation)) {
  model_summary <- summary(models_moderation[[i]])
  
    count_model_coef <- as.data.frame(model_summary$coefficients$count)
  count_model_coef$Predictor <- predictors[i]
  count_model_coef$Model <- "Count Model"   
  count_model_coef <- count_model_coef %>% 
    filter(row.names(.) != "(Intercept)") %>%   
    rename(Coefficient = Estimate, SE = `Std. Error`, pval = `Pr(>|z|)`)
  
  zero_hurdle_coef <- as.data.frame(model_summary$coefficients$zero)
  zero_hurdle_coef$Predictor <- predictors[i]
  zero_hurdle_coef$Model <- "Zero Hurdle Model"   
  zero_hurdle_coef <- zero_hurdle_coef %>% 
    filter(row.names(.) != "(Intercept)") %>%   
    rename(Coefficient = Estimate, SE = `Std. Error`, pval = `Pr(>|z|)`)
  
  model_frames_moderation[[i]] <- rbind(count_model_coef, zero_hurdle_coef)
}

combined_df_moderation <- bind_rows(model_frames_moderation) %>%
  mutate(Significance = ifelse(pval < 0.05, "sig.", "insig."),
         Predictor = fct_inorder(rev(Predictor))) %>%
  group_by(Model) %>%
  mutate(AlphaValue = abs(Coefficient) / max(abs(Coefficient), na.rm = TRUE)) %>%
  ungroup()

comment_plot_pred_m <- ggplot(combined_df_moderation, aes(x = rev(Predictor), alpha = AlphaValue)) +
  geom_hline(yintercept = 0, colour = gray(1/2), lty = 2) +
  geom_pointrange(aes(y = Coefficient, ymin = Coefficient - SE * interval2,
                      ymax = Coefficient + SE * interval2), colour = "#6699FF", lwd = 1) +
  guides(alpha = "none") +
  theme_bw(base_size = 10) +
  coord_flip() +
  facet_wrap(~ Model, ncol = 2, scales = "free_x") +
  ggtitle("Moderation condition", subtitle = "Prediction of user level discussion participation") +
  xlab("") +
  ylab("Zero hurdle models for count data regression")


# filtered data for incentives condition
scaled_sample_i <- present_sample %>% filter(condition == "incentives")

# Models for incentives condition
models_incentives <- list(
  hurdle(comment_count ~ gender_male, data = scaled_sample_i),
  hurdle(comment_count ~ age, data = scaled_sample_i),
  hurdle(comment_count ~ education, data = scaled_sample_i),
  hurdle(comment_count ~ comments_online_w1, data = scaled_sample_i),
  hurdle(comment_count ~ comment_karma, data = scaled_sample_i),
  hurdle(comment_count ~ leftright_w1, data = scaled_sample_i),
  hurdle(comment_count ~ polinterest_w1, data = scaled_sample_i),
  hurdle(comment_count ~ affective_polarization_w1, data = scaled_sample_i),
  hurdle(comment_count ~ trust_general_1_w1, data = scaled_sample_i),
  hurdle(comment_count ~ trust_general_2_w1, data = scaled_sample_i),
  hurdle(comment_count ~ trust_general_3_w1, data = scaled_sample_i),
  hurdle(comment_count ~ trust_general_4_w1, data = scaled_sample_i),
  hurdle(comment_count ~ mean_issue_distance_abs, data = scaled_sample_i),
  hurdle(comment_count ~ mean_group_respectful, data = scaled_sample_i),
  hurdle(comment_count ~ mean_group_knowledgeable, data = scaled_sample_i),
  hurdle(comment_count ~ mean_group_polarized, data = scaled_sample_i),
  hurdle(comment_count ~ mean_discussion_enjoyable, data = scaled_sample_i),
  hurdle(comment_count ~ mean_discussion_toxic, data = scaled_sample_i),
  hurdle(comment_count ~ mean_discussion_constructive, data = scaled_sample_i)
)


model_frames_incentives <- list()
for (i in seq_along(models_incentives)) {
  model_summary <- summary(models_incentives[[i]])
  
  count_model_coef <- as.data.frame(model_summary$coefficients$count)
  count_model_coef$Predictor <- predictors[i]
  count_model_coef$Model <- "Count Model"   
  count_model_coef <- count_model_coef %>% 
    filter(row.names(.) != "(Intercept)") %>%   
    rename(Coefficient = Estimate, SE = `Std. Error`, pval = `Pr(>|z|)`)
  
  zero_hurdle_coef <- as.data.frame(model_summary$coefficients$zero)
  zero_hurdle_coef$Predictor <- predictors[i]
  zero_hurdle_coef$Model <- "Zero Hurdle Model"   
  zero_hurdle_coef <- zero_hurdle_coef %>% 
    filter(row.names(.) != "(Intercept)") %>%   
    rename(Coefficient = Estimate, SE = `Std. Error`, pval = `Pr(>|z|)`)
  
  model_frames_incentives[[i]] <- rbind(count_model_coef, zero_hurdle_coef)
}

combined_df_incentives <- bind_rows(model_frames_incentives) %>%
  mutate(Significance = ifelse(pval < 0.05, "sig.", "insig."),
         Predictor = fct_inorder(rev(Predictor))) %>%
  group_by(Model) %>%
  mutate(AlphaValue = abs(Coefficient) / max(abs(Coefficient), na.rm = TRUE)) %>%
  ungroup()

comment_plot_pred_i <- ggplot(combined_df_incentives, aes(x = rev(Predictor), alpha = AlphaValue)) +
  geom_hline(yintercept = 0, colour = gray(1/2), lty = 2) +
  geom_pointrange(aes(y = Coefficient, ymin = Coefficient - SE * interval2,
                      ymax = Coefficient + SE * interval2), colour = "#29c195", lwd = 1) +
  guides(alpha = "none") +
  theme_bw(base_size = 10) +
  coord_flip() +
  facet_wrap(~ Model, ncol = 2, scales = "free_x") +
  ggtitle("Incentives condition", subtitle = "Prediction of user level discussion participation") +
  xlab("") +
  ylab("Zero hurdle models for count data regression")

combi_conditions <- grid.arrange(comment_plot_pred_c, comment_plot_pred_m, comment_plot_pred_i, nrow = 3)

ggsave("../output/combi_comment_plot_pred_conditions_hurdle.pdf", combi_conditions, width = 8, height = 12)
```

## Hurdle models for different conditions simple for main manuscript
```{r, fig.width=12, fig.height=3}
present_sample <- scaled_sample%>%filter(active2 != "inactive")

# filtered data for control condition
scaled_sample_c <- present_sample %>% filter(condition == "control")

models_control <- list(
  hurdle(comment_count ~ gender_male, data = scaled_sample_c),
  hurdle(comment_count ~ polinterest_w1, data = scaled_sample_c),
  hurdle(comment_count ~ mean_group_knowledgeable, data = scaled_sample_c),
  hurdle(comment_count ~ mean_discussion_toxic, data = scaled_sample_c)
)

predictors <- c("Gender (male)",  "Political interest", 
                "Group knowledgeable", "Discussion toxic")

model_frames_control <- list()

for (i in seq_along(models_control)) {
  model_summary <- summary(models_control[[i]])
  
  count_model_coef <- as.data.frame(model_summary$coefficients$count)
  count_model_coef$Predictor <- predictors[i]
  count_model_coef$Model <- "Count Model"   
  count_model_coef <- count_model_coef %>% 
    filter(row.names(.) != "(Intercept)") %>%   
    rename(Coefficient = Estimate, SE = `Std. Error`, pval = `Pr(>|z|)`)
  
  zero_hurdle_coef <- as.data.frame(model_summary$coefficients$zero)
  zero_hurdle_coef$Predictor <- predictors[i]
  zero_hurdle_coef$Model <- "Zero Hurdle Model"   
  zero_hurdle_coef <- zero_hurdle_coef %>% 
    filter(row.names(.) != "(Intercept)") %>%   
    rename(Coefficient = Estimate, SE = `Std. Error`, pval = `Pr(>|z|)`)
  
  model_frames_control[[i]] <- rbind(count_model_coef, zero_hurdle_coef)
}

combined_df_control <- bind_rows(model_frames_control) %>%
  mutate(Significance = ifelse(pval < 0.05, "sig.", "insig."),
         Predictor = fct_inorder(rev(Predictor))) %>%
  group_by(Model) %>%
  mutate(AlphaValue = abs(Coefficient) / max(abs(Coefficient), na.rm = TRUE)) %>%
  ungroup()

comment_plot_pred_c <- ggplot(combined_df_control, aes(x = rev(Predictor), alpha = AlphaValue)) +
  geom_hline(yintercept = 0, colour = gray(1/2), lty = 2) +
  geom_pointrange(aes(y = Coefficient, ymin = Coefficient - SE * interval2,
                      ymax = Coefficient + SE * interval2), colour = "#70facb", lwd = 1) +
  guides(alpha = "none") +
  theme_bw(base_size = 10) +
  coord_flip() +
  facet_wrap(~ Model, ncol = 2, scales = "free_x") +
  ggtitle("Control condition", subtitle = "Prediction of discussion participation") +
  xlab("") +
  ylab("")

# filtered data for moderation condition
scaled_sample_m <- present_sample %>% filter(condition == "moderation")

models_moderation <- list(
  hurdle(comment_count ~ gender_male, data = scaled_sample_m),
  hurdle(comment_count ~ polinterest_w1, data = scaled_sample_m),
  hurdle(comment_count ~ mean_group_knowledgeable, data = scaled_sample_m),
  hurdle(comment_count ~ mean_discussion_toxic, data = scaled_sample_m)
)


model_frames_moderation <- list()
for (i in seq_along(models_moderation)) {
  model_summary <- summary(models_moderation[[i]])
  
    count_model_coef <- as.data.frame(model_summary$coefficients$count)
  count_model_coef$Predictor <- predictors[i]
  count_model_coef$Model <- "Count Model"   
  count_model_coef <- count_model_coef %>% 
    filter(row.names(.) != "(Intercept)") %>%   
    rename(Coefficient = Estimate, SE = `Std. Error`, pval = `Pr(>|z|)`)
  
  zero_hurdle_coef <- as.data.frame(model_summary$coefficients$zero)
  zero_hurdle_coef$Predictor <- predictors[i]
  zero_hurdle_coef$Model <- "Zero Hurdle Model"   
  zero_hurdle_coef <- zero_hurdle_coef %>% 
    filter(row.names(.) != "(Intercept)") %>%   
    rename(Coefficient = Estimate, SE = `Std. Error`, pval = `Pr(>|z|)`)
  
  model_frames_moderation[[i]] <- rbind(count_model_coef, zero_hurdle_coef)
}

combined_df_moderation <- bind_rows(model_frames_moderation) %>%
  mutate(Significance = ifelse(pval < 0.05, "sig.", "insig."),
         Predictor = fct_inorder(rev(Predictor))) %>%
  group_by(Model) %>%
  mutate(AlphaValue = abs(Coefficient) / max(abs(Coefficient), na.rm = TRUE)) %>%
  ungroup()

comment_plot_pred_m <- ggplot(combined_df_moderation, aes(x = rev(Predictor))) +
  geom_hline(yintercept = 0, colour = gray(1/2), lty = 2) +
  geom_pointrange(aes(y = Coefficient, ymin = Coefficient - SE * interval2,
                      ymax = Coefficient + SE * interval2), colour = "#6699FF", lwd = 1) +
  guides(alpha = "none") +
  theme_bw(base_size = 10) +
  coord_flip() +
  facet_wrap(~ Model, ncol = 2, scales = "free_x") +
  ggtitle("Moderation condition", subtitle = "Prediction of discussion participation") +
  xlab("") +
  ylab("")

# filtered data for incentives condition
scaled_sample_i <- present_sample %>% filter(condition == "incentives")

models_incentives <- list(
  hurdle(comment_count ~ gender_male, data = scaled_sample_i),
  hurdle(comment_count ~ polinterest_w1, data = scaled_sample_i),
  hurdle(comment_count ~ mean_group_knowledgeable, data = scaled_sample_i),
  hurdle(comment_count ~ mean_discussion_toxic, data = scaled_sample_i)
)


model_frames_incentives <- list()
for (i in seq_along(models_incentives)) {
  model_summary <- summary(models_incentives[[i]])
  
  count_model_coef <- as.data.frame(model_summary$coefficients$count)
  count_model_coef$Predictor <- predictors[i]
  count_model_coef$Model <- "Count Model"   
  count_model_coef <- count_model_coef %>% 
    filter(row.names(.) != "(Intercept)") %>%   
    rename(Coefficient = Estimate, SE = `Std. Error`, pval = `Pr(>|z|)`)
  
  zero_hurdle_coef <- as.data.frame(model_summary$coefficients$zero)
  zero_hurdle_coef$Predictor <- predictors[i]
  zero_hurdle_coef$Model <- "Zero Hurdle Model"   
  zero_hurdle_coef <- zero_hurdle_coef %>% 
    filter(row.names(.) != "(Intercept)") %>%   
    rename(Coefficient = Estimate, SE = `Std. Error`, pval = `Pr(>|z|)`)
  
  model_frames_incentives[[i]] <- rbind(count_model_coef, zero_hurdle_coef)
}

combined_df_incentives <- bind_rows(model_frames_incentives) %>%
  mutate(Significance = ifelse(pval < 0.05, "sig.", "insig."),
         Predictor = fct_inorder(rev(Predictor))) %>%
  group_by(Model) %>%
  mutate(AlphaValue = abs(Coefficient) / max(abs(Coefficient), na.rm = TRUE)) %>%
  ungroup()

comment_plot_pred_i <- ggplot(combined_df_incentives, aes(x = rev(Predictor))) +
  geom_hline(yintercept = 0, colour = gray(1/2), lty = 2) +
  geom_pointrange(aes(y = Coefficient, ymin = Coefficient - SE * interval2,
                      ymax = Coefficient + SE * interval2), colour = "#29c195", lwd = 1) +
  guides(alpha = "none") +
  theme_bw(base_size = 10) +
  coord_flip() +
  facet_wrap(~ Model, ncol = 2, scales = "free_x") +
  ggtitle("Incentives condition",subtitle = "Prediction of discussion participation") +
  xlab("") +
  ylab("")

combi_conditions <- grid.arrange(comment_plot_pred_m, comment_plot_pred_i, nrow = 1)

ggsave("../output/combi_comment_plot_pred_conditions_hurdle_simple.pdf", combi_conditions, width = 10, height = 3)
```

## Baseline Balance 
```{r}
# variables balance table
covariates <- c("age", "gender", "education","time_online_w1" , "social_media_w1" , "comments_online_w1" ,
 "leftright_w1"                  ,  "polinterest_w1"                , "affective_pol_1_w1"             ,
 "affective_pol_2_w1"            ,  "issue_attitudes_loan_w1"       , "issue_attitudes_airbnb_w1"      ,
 "issue_attitudes_minwage_w1"    ,  "issue_attitudes_ukraine_w1"    , "issue_attitudes_ubi_w1"         ,
 "issue_attitudes_climate_w1"    ,  "issue_attitudes_fur_w1"        , "issue_attitudes_renewable_w1"   ,
 "issue_attitudes_gaza_w1"       ,  "issue_attitudes_vegetarian_w1" , "issue_attitudes_gender_w1"      ,
 "issue_attitudes_sexwork_w1"    ,  "issue_attitudes_vaccine_w1"    , "issue_attitudes_healthcare_w1"  ,
 "issue_attitudes_immigration_w1",  "issue_attitudes_guns_w1"       , "issue_attitudes_deathpenalty_w1",
 "issue_attitudes_bodycams_w1"   ,  "issue_attitudes_ai_w1"         , "issue_attitudes_socialmedia_w1" ,
 "issue_knowledge_loan_w1"       ,  "issue_knowledge_airbnb_w1"     , "issue_knowledge_minwage_w1"     ,
 "issue_knowledge_ukraine_w1"    ,  "issue_knowledge_ubi_w1"        , "issue_knowledge_climate_w1"     ,
 "issue_knowledge_fur_w1"        ,  "issue_knowledge_renewable_w1"  , "issue_knowledge_mideast_w1"     ,
 "issue_knowledge_vegetarian_w1" ,  "issue_knowledge_gender_w1"     , "issue_knowledge_sexwork_w1"     ,
 "issue_knowledge_vaccine_w1"    ,  "issue_knowledge_healthcare_w1" , "issue_knowledge_immigration_w1" ,
 "issue_knowledge_guns_w1"       ,  "issue_knowledge_deathpenalty_w1", "issue_knowledge_bodycams_w1"    ,
 "issue_knowledge_ai_w1"         ,  "issue_knowledge_socialmedia_w1", "political_efficacy_1_w1"        ,
 "political_efficacy_2_w1"       ,  "political_efficacy_3_w1"       , "trust_general_1_w1"             ,
 "trust_general_2_w1"            ,  "trust_general_3_w1"            , "trust_general_4_w1"             ,
 "pol_cynicism_w1", "affective_polarization_w1"  ,     "efficacy_w1" ,"comment_karma","comment_count" ,                  "comment_mean_lenght"   ,   "comment_mean_score"  ,     "comment_mean_tox"  ,  "ex_comment_count",  "ex_comment_mean_score"  ,  "ex_comment_mean_tox"  ,    "ex_comment_mean_lenght"  )

table1 <- CreateTableOne(vars = covariates, strata = "condition", data = full_data)

latex_table <- print(table1, smd = TRUE, printToggle = FALSE)
rownames(latex_table) <- gsub("\\(mean \\(SD\\)\\)", "", rownames(latex_table))

knitr::kable(latex_table[, -grep("test", colnames(latex_table))], 
                      format = "html", booktabs = TRUE)

```



# WS: Compare inactive to "active"-but-never-commented

```{r}
#toplot <- present_sample %>% mutate(ever_comment = comment_count>0) %>% group_by(gender_male, ever_comment) %>% count

test <- scaled_sample %>% filter(active == 0) %>% mutate(inactive = (active2=="inactive"))

test$trust_general_4_w1

#logistic regression to identify predictors of inactivity
logit_model <- glm(inactive ~ gender_male + age + polinterest_w1 + comments_online_w1 + education + trust_general_4_w1, data = test, family = binomial(link = "logit"))

logit_model %>% summary

```


```{r}


```


```{r}


```


```{r}


```


# WS: Investigating Affpol & Ideological Extremity

```{r}
full_data$affective_polarization_w1
full_data$leftright_w1
full_data$polinterest_w1
full_data$affective_pol_1_w1
full_data$affective_pol_2_w1

full_data
```


```{r}
#plot(full_data$polinterest_w1, scaled_sample$affective_polarization_w1)

plot(full_data$leftright_w1, scaled_sample$affective_polarization_w1)

```

## How is affpol coded?

```{r}
plot(full_data$leftright_w1, full_data$affective_pol_1_w1) #affective_pol_1_w1 is warmth towards dems
plot(full_data$leftright_w1, full_data$affective_pol_2_w1) #affective_pol_2_w1 is warmth towards reps
```


```{r}
plot(full_data$affective_polarization_w1, (full_data$affective_pol_1_w1-full_data$affective_pol_2_w1))

#so affective_polarization_w1 is ingroup favoritism
```


```{r}
plot(scaled_sample$affective_polarization_w1, scaled_sample$comment_count)
plot(scaled_sample$polinterest_w1, scaled_sample$comment_count)

```

# WS: PCA Issue Ideo Analysis

```{r}
ideo_pca <- psych::pca(pre_survey %>% select(starts_with("issue_attitudes_")), nfactors = 1)
ideo_pca

#extract scores and join them to pre_survey
pre_survey <- cbind(pre_survey, ideo_pca$scores)

```


```{r}
scaled_sample <- left_join(scaled_sample, pre_survey %>% select(ParticipantID, RC1, RC2), by = "ParticipantID")

plot(scaled_sample$RC1, scaled_sample$comment_count)

lm(comment_count ~ abs(RC1), data = scaled_sample) %>% summary

```


```{r}


```


```{r}


```


```{r}


```


```{r}


```


```{r}


```


```{r}


```


```{r}


```


```{r}


```


```{r}


```


```{r}


```


```{r}


```


```{r}


```


```{r}


```


```{r}


```


```{r}


```


```{r}


```


```{r}


```


```{r}


```


```{r}


```


```{r}


```


```{r}


```


```{r}


```


```{r}


```


```{r}


```


```{r}


```


```{r}


```


```{r}


```


```{r}


```


```{r}


```


```{r}


```


```{r}


```


```{r}


```


```{r}


```


```{r}


```


```{r}


```


```{r}


```


```{r}


```


```{r}


```


```{r}


```


```{r}


```


```{r}


```


```{r}


```


```{r}


```


```{r}


```


