---
title: "Comment Plot"
subtitle: "Reddit Communities Field Experiment"
output: html_document
date: "`r Sys.Date()`"
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = T, out.width = "100%", out.height = "30%", message=F, warning=F)
```

```{r}
library(tidyverse)
library(lubridate)
```

Load anonymous data (no comment texts, open comments, usernames or email addresses)
```{r , results='hide'}
# reddit data
discussion_data <- read_csv("../data/anon/discussions_anon.csv")
sample <- read_csv("../data/anon/sample_anon.csv")
```


# Prep the Data

```{r}
# here I make a version of internal_comments that is "augmented" with additional variables from the survey, and additional variables constructed below
internal_comments_augmented <- discussion_data %>% mutate(source = "internal")%>%
  filter(created_comment > as_datetime("2024-06-10") & created_comment < as_datetime("2024-07-06")) %>%
  filter(!is.na(ParticipantID))
internal_comments_augmented <- left_join(internal_comments_augmented %>% select(-"subreddit", -"...1"), sample, by = "ParticipantID")
internal_comments_augmented <- internal_comments_augmented %>% filter(!is.na(condition), !is.na(ParticipantID), !is.na(subreddit))
#internal_comments_augmented <- left_join(internal_comments, s, by = "ParticipantID")

# rescale toxicity to 0,1
toxicity_quantiles <- internal_comments_augmented$comment_toxicity %>% quantile(probs = seq(0, 1, by = 0.1), na.rm = TRUE)
internal_comments_augmented <- internal_comments_augmented %>% filter(!is.na(comment_toxicity)) %>% mutate(comment_toxicity_rescaled = cut(comment_toxicity, breaks = toxicity_quantiles, labels = F, include.lowest = TRUE)/10)

```


```{r}
internal_comments_augmented %>% filter(score_comment == 0)

```


```{r}
# continue augmenting
# rescale comment_score to be most visible in the color gradient

#monotonic quantile version
score_comment_quantiles <- internal_comments_augmented$score_comment %>% quantile(probs = seq(0, 1, by = 0.25), na.rm = TRUE)
internal_comments_augmented <- internal_comments_augmented %>% mutate(score_comment_rescaled_quantile = cut(score_comment, breaks = score_comment_quantiles, labels = F, include.lowest = TRUE)/4)

#simple version
internal_comments_augmented <- internal_comments_augmented %>% mutate(score_comment_rescaled = (score_comment - min(score_comment))/(max(score_comment) - min(score_comment)))

#polar version
scale_polar_to_01 <- function(x) {
  
  # Initialize vector to hold rescaled values
  x_scaled <- numeric(length(x))
  
  # Identify the minimum of negatives and maximum of positives
  min_neg <- min(x[x < 0], na.rm = TRUE)
  max_pos <- max(x[x > 0], na.rm = TRUE)
  
  # Rescale negatives to [0, 0.5)
  # Map from [min_neg, 0] --> [0, 0.5)
  x_scaled[x < 0] <- 0.5 * (x[x < 0] - min_neg) / (0 - min_neg)
  
  # Any exact zeros go to 0.5
  x_scaled[x == 0] <- 0.5
  
  # Rescale positives to (0.5, 1]
  # Map from [0, max_pos] --> [0.5, 1]
  x_scaled[x > 0] <- 0.5 + 0.5 * (x[x > 0] / max_pos)
  
  return(x_scaled)
}

internal_comments_augmented <- internal_comments_augmented %>% mutate(score_comment_rescaled_polar = scale_polar_to_01(score_comment))


hist(internal_comments_augmented$score_comment_rescaled)
hist(internal_comments_augmented$score_comment_rescaled_polar)
```


```{r}
# continue augmenting
# add rescaled length of comment

length_comment_char_quantiles <- internal_comments_augmented$length_comment_char %>% quantile(probs = seq(0, 1, by = 0.1), na.rm = TRUE)

internal_comments_augmented <- internal_comments_augmented %>% filter(!is.na(length_comment_char)) %>% mutate(length_comment_char_rescaled = cut(length_comment_char, breaks = length_comment_char_quantiles, labels = F, include.lowest = TRUE)/10)

# add first and last comment datetimes
internal_comments_augmented <- left_join(internal_comments_augmented, (internal_comments_augmented %>% group_by(ParticipantID) %>% dplyr::summarize(first_comment_posted = min(created_comment), last_comment_posted = max(created_comment))))
```


# Write Plotting Functions

```{r}
# Functinos for making the comment plot

color_interpolate <- function(color1, color2, value){
  color1 <- col2rgb(color1)
  color2 <- col2rgb(color2)
  color <- color1 + (color2 - color1) * value
  return(rgb(color[1], color[2], color[3], maxColorValue = 255))
}


plot_comments <- function(data, names_for_participant_heights, color_column, main, color1 = "green", color2 = "red", pch = "|", bg = "black", fg = "white", xlim = NULL, point_size = 1){
  # Filter data to remove NA toxicity values
  data <- data
  names_for_participant_heights <- names_for_participant_heights[which(names_for_participant_heights %in% data$ParticipantID)]
  participant_heights <- 1:length(names_for_participant_heights)
  names(participant_heights) <- names_for_participant_heights
  par(bg = bg)
  par(bg = bg, col.axis = fg, col.lab = fg, col.main = fg, col.sub = fg)
  
  if(is.null(xlim)){
    xlim <- c(min(data$created_comment), max(data$created_comment))
  }
  
  color_column_sym <- sym(color_column)
  
  # Initialize the plot
  plot(data$created_comment[1], participant_heights[which(names(participant_heights) == data$ParticipantID[1])], 
       type = "p", pch = pch, col = rgb(0, 0, 0, 0), 
       xlab = "Date", ylab = "ParticipantID", 
       ylim = c(0, length(participant_heights)), 
       xlim = xlim, 
       main = main, 
       yaxt = "n")
  
  # Add vertical lines at midnight Pacific time
  date_range <- c(lubridate::floor_date(min(data$created_comment), unit = "day"), 
                  lubridate::ceiling_date(max(data$created_comment), unit = "day"))
  date_range <- seq(date_range[1], date_range[2], by = "day")
  date_range_pacific <- with_tz(date_range, tzone = "America/Los_Angeles")
  for(i in date_range_pacific){
    abline(v = i, col = rgb(1, 1, 1, .2), lty = 1)
  }
  
  # Plot posts in rows with adjustable point size
  for(i in 1:nrow(data)){
    points(data$created_comment[i], 
           participant_heights[which(names(participant_heights) == data$ParticipantID[i])], 
           type = "p", pch = pch, 
           col = color_interpolate(color1, color2, data[[color_column_sym]][i]), 
           cex = point_size) # Adjust point size here
  }
  
  # Annotate each row with the ParticipantID in small text right-aligned to the y-axis
  par(xpd = TRUE)
  for(i in participant_heights){
    text(x = xlim[1], y = i, labels = names(participant_heights)[i], pos = 2, cex = 0.5, col = fg)
  }
  par(xpd = FALSE)
  
  axis(1, col = fg, col.axis = NA, col.ticks = NA) # X-axis
}


# Function to create a gradient legend
add_gradient_legend <- function(color1, color2, labels = c("non-toxic", "toxic"), x, y, width, height) {
  # Generate a sequence of colors for the gradient
  n_colors <- 100
  gradient_colors <- sapply(seq(0, 1, length.out = n_colors), function(value) {
    color_interpolate(color1, color2, value)
  })
  
  # Create an image with the gradient
  par(xpd = TRUE) # Allow plotting outside the main plot
  image(
    x = seq(x, x + width, length.out = n_colors), 
    y = c(y, y + height), 
    z = matrix(seq(0, 1, length.out = n_colors), ncol = 1),
    col = gradient_colors,
    add = TRUE
  )
  
  # Add labels for the gradient
  text(x = x, y = y + height / 2, labels = labels[1], pos = 2, cex = 0.8, col = "white") # Left label
  text(x = x + width, y = y + height / 2, labels = labels[2], pos = 4, cex = 0.8, col = "white") # Right label
  par(xpd = FALSE) # Restore default plotting behavior
}

```


# Make the Plots

## Color by Toxicity

This is the version of the plot I previously shared.  Note that toxicity is rescaled using a quantile function, to show maximum variation, although we should always bear in mind that toxicity levels were low in absolute terms, so even the reddest-colored posts aren't necessarily all that toxic.

```{r, fig.height=18, fig.width=12}
# these are high-level settings for the plot:
par(mfrow = c(3,2), cex = .8)
bgcol = "black"
fgcol = "white"
pch = "|"
this_point_size = .7

this_xlim = c(lubridate::floor_date(min(internal_comments_augmented$created_comment), unit = "day"), lubridate::ceiling_date(max(internal_comments_augmented$created_comment), unit = "day"))

# Here we color the comments by their toxicity
this_color_column <- "comment_toxicity_rescaled"
color1 = "green"
color2 = "red"

#Exclude any posts with NA toxicity
filtered_data <- internal_comments_augmented %>% filter(!is.na(comment_toxicity))

# And order the participants by the time of their last comment
participant_order <- filtered_data %>% arrange(last_comment_posted) %>% pull(ParticipantID) %>% unique()

## You can also arrange the participants by another grouping variable, for example to compare male and female participants:
# filtered_data <- internal_comments_augmented %>% filter(!is.na(comment_toxicity)) %>% filter(gender %in% c(1,2))
# participant_order <- filtered_data %>% arrange(gender, last_comment_posted) %>% pull(ParticipantID) %>% unique()

control_1 <- filtered_data %>% filter(subreddit == "DiscussPolitics1")
control_6 <- filtered_data %>% filter(subreddit == "DiscussPolitics6")
moderation_2 <- filtered_data %>% filter(subreddit == "DiscussPolitics2")
moderation_5 <- filtered_data %>% filter(subreddit == "DiscussPolitics5")
incentives_3 <- filtered_data %>% filter(subreddit == "DiscussPolitics3")
incentives_4 <- filtered_data %>% filter(subreddit == "DiscussPolitics4")

plot_comments(control_1,
              names_for_participant_heights = participant_order,
              color_column = this_color_column, main = "Control A", bg = bgcol, fg = fgcol, pch = pch, color1 = color1, color2 = color2, xlim = this_xlim, point_size = this_point_size)
plot_comments(control_6,
              names_for_participant_heights = participant_order,
              color_column = this_color_column, main = "Control B", bg = bgcol, fg = fgcol, pch = pch, color1 = color1, color2 = color2, xlim = this_xlim, point_size = this_point_size)

plot_comments(moderation_2,
              names_for_participant_heights = participant_order,
              color_column = this_color_column, main = "Moderation A", bg = bgcol, fg = fgcol, pch = pch, color1 = color1, color2 = color2, xlim = this_xlim, point_size = this_point_size)
plot_comments(moderation_5,
              names_for_participant_heights = participant_order,
              color_column = this_color_column, main = "Moderation B", bg = bgcol, fg = fgcol, pch = pch, color1 = color1, color2 = color2, xlim = this_xlim, point_size = this_point_size)

plot_comments(incentives_3,
              names_for_participant_heights = participant_order,
              color_column = this_color_column, main = "Incentives A", bg = bgcol, fg = fgcol, pch = pch, color1 = color1, color2 = color2, xlim = this_xlim, point_size = this_point_size)
plot_comments(incentives_4,
              names_for_participant_heights = participant_order,
              color_column = this_color_column, main = "Incentives B", bg = bgcol, fg = fgcol, pch = pch, color1 = color1, color2 = color2, xlim = this_xlim, point_size = this_point_size)

# Add the gradient legend
add_gradient_legend(
  color1 = "green", 
  color2 = "red", 
  x = mean(filtered_data$created_comment), 
  y = 0,
  width = diff(range(filtered_data$created_comment)) / 5, 
  height = 1
)

```


## Color by Score

Here's a version of the plot that colors the comments by their score.  Right now it's showing a quantile-based rescaling of each posts' score, similar to how toxicity was rescaled.  We could also try coloring by the running mean of past scores, which is the variable that was found predictive in the temporal model.

```{r, fig.height=18, fig.width=12}
par(mfrow = c(3,2), cex = .8)
bgcol = "black"
fgcol = "white"
pch = "|"
this_point_size = .7

this_xlim = c(lubridate::floor_date(min(internal_comments_augmented$created_comment), unit = "day"), lubridate::ceiling_date(max(internal_comments_augmented$created_comment), unit = "day"))

this_color_column <- "score_comment_rescaled_quantile"
color1 = "dodgerblue"
color2 = "gold"

filtered_data <- internal_comments_augmented %>% filter(!is.na(score_comment))
participant_order <- filtered_data %>% arrange(last_comment_posted) %>% pull(ParticipantID) %>% unique()

control_1 <- filtered_data %>% filter(subreddit == "DiscussPolitics1")
control_6 <- filtered_data %>% filter(subreddit == "DiscussPolitics6")
moderation_2 <- filtered_data %>% filter(subreddit == "DiscussPolitics2")
moderation_5 <- filtered_data %>% filter(subreddit == "DiscussPolitics5")
incentives_3 <- filtered_data %>% filter(subreddit == "DiscussPolitics3")
incentives_4 <- filtered_data %>% filter(subreddit == "DiscussPolitics4")

plot_comments(control_1,
              names_for_participant_heights = participant_order,
              color_column = this_color_column, main = "Control A", bg = bgcol, fg = fgcol, pch = pch, color1 = color1, color2 = color2, xlim = this_xlim, point_size = this_point_size)
plot_comments(control_6,
              names_for_participant_heights = participant_order,
              color_column = this_color_column, main = "Control B", bg = bgcol, fg = fgcol, pch = pch, color1 = color1, color2 = color2, xlim = this_xlim, point_size = this_point_size)

plot_comments(moderation_2,
              names_for_participant_heights = participant_order,
              color_column = this_color_column, main = "Moderation A", bg = bgcol, fg = fgcol, pch = pch, color1 = color1, color2 = color2, xlim = this_xlim, point_size = this_point_size)
plot_comments(moderation_5,
              names_for_participant_heights = participant_order,
              color_column = this_color_column, main = "Moderation B", bg = bgcol, fg = fgcol, pch = pch, color1 = color1, color2 = color2, xlim = this_xlim, point_size = this_point_size)

plot_comments(incentives_3,
              names_for_participant_heights = participant_order,
              color_column = this_color_column, main = "Incentives A", bg = bgcol, fg = fgcol, pch = pch, color1 = color1, color2 = color2, xlim = this_xlim, point_size = this_point_size)
plot_comments(incentives_4,
              names_for_participant_heights = participant_order,
              color_column = this_color_column, main = "Incentives B", bg = bgcol, fg = fgcol, pch = pch, color1 = color1, color2 = color2, xlim = this_xlim, point_size = this_point_size)

# Add the gradient legend
add_gradient_legend(labels = c("Low", "High"),
  color1 = "dodgerblue", 
  color2 = "gold", 
  x = mean(filtered_data$created_comment), 
  y = 0,
  width = diff(range(filtered_data$created_comment)) / 5, 
  height = 1
)

```


## Export PDF


```{r, fig.height=12, fig.width=12}
#save PDF

pdf("ws_outputs/plot_comments_toxicity.pdf", width = 12, height = 21)
# #apply to each dataframe, layout 2*3
par(mfrow = c(3,2), cex = .8)
bgcol = "black"
fgcol = "white"
pch = "|"
this_point_size = .8

this_xlim = c(lubridate::floor_date(min(internal_comments_augmented$created_comment), unit = "day"), lubridate::ceiling_date(max(internal_comments_augmented$created_comment), unit = "day"))

this_color_column <- "comment_toxicity_rescaled"
color1 = "green"
color2 = "red"

filtered_data <- internal_comments_augmented
participant_order <- filtered_data %>% arrange(last_comment_posted) %>% pull(ParticipantID) %>% unique()

control_1 <- filtered_data %>% filter(subreddit == "DiscussPolitics1")
control_6 <- filtered_data %>% filter(subreddit == "DiscussPolitics6")
moderation_2 <- filtered_data %>% filter(subreddit == "DiscussPolitics2")
moderation_5 <- filtered_data %>% filter(subreddit == "DiscussPolitics5")
incentives_3 <- filtered_data %>% filter(subreddit == "DiscussPolitics3")
incentives_4 <- filtered_data %>% filter(subreddit == "DiscussPolitics4")

plot_comments(control_1,
              names_for_participant_heights = participant_order,
              color_column = this_color_column, main = "Control A", bg = bgcol, fg = fgcol, pch = pch, color1 = color1, color2 = color2, xlim = this_xlim, point_size = this_point_size)
plot_comments(control_6,
              names_for_participant_heights = participant_order,
              color_column = this_color_column, main = "Control B", bg = bgcol, fg = fgcol, pch = pch, color1 = color1, color2 = color2, xlim = this_xlim, point_size = this_point_size)

plot_comments(moderation_2,
              names_for_participant_heights = participant_order,
              color_column = this_color_column, main = "Moderation A", bg = bgcol, fg = fgcol, pch = pch, color1 = color1, color2 = color2, xlim = this_xlim, point_size = this_point_size)
plot_comments(moderation_5,
              names_for_participant_heights = participant_order,
              color_column = this_color_column, main = "Moderation B", bg = bgcol, fg = fgcol, pch = pch, color1 = color1, color2 = color2, xlim = this_xlim, point_size = this_point_size)

plot_comments(incentives_3,
              names_for_participant_heights = participant_order,
              color_column = this_color_column, main = "Incentives A", bg = bgcol, fg = fgcol, pch = pch, color1 = color1, color2 = color2, xlim = this_xlim, point_size = this_point_size)
plot_comments(incentives_4,
              names_for_participant_heights = participant_order,
              color_column = this_color_column, main = "Incentives B", bg = bgcol, fg = fgcol, pch = pch, color1 = color1, color2 = color2, xlim = this_xlim, point_size = this_point_size)

# Add the gradient legend
add_gradient_legend(
  color1 = "green", 
  color2 = "red", 
  x = mean(filtered_data$created_comment), 
  y = 0,
  width = diff(range(filtered_data$created_comment)) / 5, 
  height = 1
)


dev.off()

```

# Other Stuff

We might be interested in the fraction of comments each user accounts for on their subreddit:

```{r}
# Fraction of comments each user accounts for on their subreddit
internal_comments_augmented %>% filter(subreddit=="DiscussPolitics1") %>% group_by(ParticipantID) %>% dplyr::summarize(n = n(), frac = n()/nrow(.)) %>% pull(frac) %>% hist

```



